\cvsection{Education}
\begin{cventries}
  \cventry
    {M.S. (Ing.) in Open Informatics}
    {Czech Technical University, Faculty of Electrical Engineering}
    {Prague, Czech Republic}
    {Sep 2016 - Jun 2018}
    {
      \begin{cvitems}
        \item {Computer Science and Software Engineering.}
        \item {\textbf{Summa cum laude}.}
        \item {Specialization in Software Engineering.}
      \end{cvitems}
    }

  \cventry
    {B.S. (Bc.) in Software Engineering and Management}
    {Czech Technical University, Faculty of Electrical Engineering}
    {Prague, Czech Republic}
    {Sep 2012 - Jun 2016}
    {
      \begin{cvitems}
        \item {Software Engineering specialization.}
        \item {\textbf{Summa cum laude}.}
        \item {I got to work with the following programming languages: C, C++, Java SE, Java EE, Python and SQL.}
        \item {At first, I studied Electrotechnics \& Energetics, but I transferred to Software Engineering after successfuly finishing the first year, as I discovered my passion in programming.}
      \end{cvitems}
    }

  \cventry
    {Grammar School}
    {Grammar School, Jírovcova 8, České Budějovice}
    {České Budějovice, Czech Republic}
    {Sep 2008 - Jun 2012}
    {
      \begin{cvitems}
        \item {Graduated with honors from Mathematics, Physics and Czech Language.}
        \item {Participated in student competitions in Physics, English and Biology.}
        \item {I passed exams for \textbf{First Certificate of English}, mark \textbf{A+}, guaranteeing my English is at C1 level.}
      \end{cvitems}
    }
\end{cventries}
