\cvsection{Experience}
\begin{cventries}
  \cventry
    {Engineering Manager}
    {Pure Storage}
    {Prague, Czech Republic}
    {Feb. 2024 - Present}
    {
    \begin{cvitems}
      \item {Managing two teams of software and QA engineers, 12 people in total, delivering Pure Protect (Disaster Recovery as a Service).}
      \item {Skills: People management, Project management, Release management}
      \item {Technologies: Java, Kotlin (Spring framework, Reactive streams), JavaScript (Typescript, AngularJS, RxJS), MongoDB, Apache Kafka, Docker, Kubernetes, AWS, Scrum, Github}
    \end{cvitems}
    }
  \cventry
    {Member of Technical Staff (Senior Software Engineer)}
    {Pure Storage}
    {Prague, Czech Republic}
    {Jul. 2022 - Feb. 2024}
    {
    \begin{cvitems}
      \item {Leading a team of software engineers and implementing the front-end and microservices of Pure Protect (Disaster Recovery as a Service).}
      \item {Cooperating with teams across the business unit and reporting our results to management.}
      \item {Technologies: Java, Kotlin (Spring framework, Reactive streams), JavaScript (Typescript, AngularJS, RxJS), MongoDB, Apache Kafka, Docker, Kubernetes, AWS, Scrum, Github}
    \end{cvitems}
  }
  \cventry
    {Senior Software Engineer}
    {Cogvio, s.r.o.}
    {Prague, Czech Republic}
    {Mar. 2017 - Jun. 2022}
    {
    \begin{cvitems}
      \item {Analysis, design, implementation, testing, deployment and maintenance of multiple Cogvio products, namely Price Monitor, Market Access Monitor and Patient Registry. Modelling and automatization of data processes.}
      \item {Technologies: Java 11/16 (Spring Framework, Hibernate), Kotlin, JavaScript (Typescript, React, Parcel), Python, PostgreSQL, ElasticSearch, AWS, Docker, Continuous Integration and delivery, Gitlab, Shape-up}
    \end{cvitems}
  }
  \cventry
    {Lead Software Engineer}
    {Medevio s.r.o.}
    {Prague, Czech Republic}
    {Mar. 2020 - Jun. 2021}
    {
    \begin{cvitems}
      \item {Leading the software development in Cogvio Medical. Hands-on architecture and programming of backend APIs, plus overseeing development of a web application and two mobile applications (Android and iOS).
       Helping with project and product management leveraging agile techniques.}
      \item {Technologies: Java 11 (Spring Boot, Hibernate), Kotlin, JavaScript (Typescript, React, Parcel), PostgreSQL, DynamoDB, gRPC, AWS, GCP, Docker, Terraform, Cryptography, Messaging (AWS SNS), Continuous integration and delivery, Gitlab}
    \end{cvitems}
  }
  \cventry
    {Lead Backend Developer}
    {Hiri.cz (Startupedia s.r.o.)}
    {Prague, Czech Republic}
    {Jan. 2015 - Mar. 2017}
    {
      \begin{cvitems}
        \item {Analysis, design, implementation, testing, deployment and maintenance of Hiri.cz job portal's back-end.}
        \item {I designed and lead development of REST API behind Hiri.cz SPA client. The API is responsible for business logic of the job portal and provides data persistence.}
        \item {Technologies: PHP 7 (Nette Framework, Doctrine ORM, Symfony Framework Components, Behat, Nette Tester), Javascript (Node.js), PostgreSQL, Redis}
      \end{cvitems}
    }
  \cventry
    {Full-stack Developer}
    {StartupJobs.cz (Startupedia s.r.o.)}
    {Prague, Czech Republic}
    {Nov. 2013 - Mar. 2017}
    {
      \begin{cvitems}
        \item {Development, testing, and maintenance of job portal for startups in Czech Republic.}
        \item {I lead refactoring of application's model layer from Nette Database to Doctrine ORM and I also lead refactoring of application's internal order process and connected it to a new e-payment system.}
        \item {Technologies: PHP 5/7 (Nette Framework, Doctrine ORM, Symfony Framework Components, Nette Tester, Codeception, PHPUnit), MySQL/MariaDB, HTML5, CSS (LESS), JavaScript (jQuery)}
      \end{cvitems}
    }
  \cventry
    {Full-stack Developer}
    {Geekshop.cz (Geek Distribution s.r.o.)}
    {Prague, Czech Republic}
    {Nov. 2013 - Apr. 2014}
    {
      \begin{cvitems}
        \item {Development, testing, deployment and monitoring of unique e-commerce solution for e-shop with branded clothing.}
        \item {I connected the system to a baking API, improved automatization of store process, like barcode scanning, automatic emails about order confirmation and order expedition.}
        \item {Technologies: PHP 5 (Zend Framework), MySQL, HTML, CSS, JavaScript (jQuery), Git, CentOS}
      \end{cvitems}
    }
  \cventry
    {Freelance software developer}
    {Miscellaneous}
    {Czech Republic}
    {Since Jul. 2011}
    {
      \begin{cvitems}
        \item {Throughout my career as a software developer I worked on several smaller projects, including e-commerce solutions and personal and company websites.}
        \item {The largest project was building and maintaining an e-shop for family-run business, where I got to work on all aspects of the solution, including an order and shipping system, reporting and SEO optimization.}
        \item {Technologies: PHP (Nette Framework), MySQL, Postgresql, HTML, CSS (Tailwind), JavaScript (React, jQuery), Git}
      \end{cvitems}
    }
\end{cventries}
